---
title: ""
author:
date: 
output: 
  html_document

---

```{r, include=F}
# params:
#   model.path: "./../data/out/occ_output/fm_models_out/RedFox_2018_20200606_1655"

## will probably have to do one file per study season, tricky to generalize across years..
## 
## year, species, model from meta

  # html_document:
  #   keep_md: TRUE



catch.p_map<-function(x){
  tryCatch({
   round(p_map(x),5)
}, warning = function(w) {
    ""
}, error = function(e) {
    "err"
})
}

catch.map_estimate<-function(x){
  tryCatch({
   round(map_estimate(x),3)
}, warning = function(w) {
    ""
}, error = function(e) {
    "err"
})
}
# Mode <- function(x) {
#   ux <- unique(x)
#   ux[which.max(tabulate(match(x, ux)))]
# }
# 
# 
# Modes <- function(x) {
#     ux <- unique(x)
#     tab <- tabulate(match(x, ux))
#     ux[tab == max(tab)]
# }



model.results<-list.files(model.path, pattern = ".RDS",full.names = T) %>%
  map(readRDS)
  # # names
out.names<-gsub(".RDS","",list.files(model.path, pattern = ".RDS"))
names(model.results)<-out.names
  
# model.results<-readRDS(params$model.results)
 #model.results <- params$model.results

#model.dat<-params$model.results
# getwd()
meta <- model.results$model.metadata
#meta<-readRDS("../../data/out/SC_model_meta_2017.Rdata")
# names(meta)

models <- c(unlist(meta$inputModels))
descriptions<- c(unlist(meta$models))
# n<-sum(c(unlist(meta$all.y.long[names(meta$all.y.long) %in% params$model.species])))
n.count<-meta$in.count
n.detections<-meta$in.detections
n.iter<-meta$n.iter
n.burn<-meta$n.burn
n.thin<-meta$n.thin
state.buffer<-meta$buffer
nSites<-meta$nSites
sigma.mean<-meta$mean.sd$out.mean
sigma.sd<-meta$mean.sd$out.sd
data.year<-meta$data.year
sp<-meta$species
cov.alpha <- meta$alpha.cov
names(cov.alpha) <- c('covariate','alpha')
cov.alpha$cov <-  paste0('alpha.ind[',c(1:8), ']')

#names(model.results)<-models

meta.summary<-tibble(n_sites = nSites, 
                     N_counts = n.count, 
                     N_detections = n.detections,
                     rep_period = '7 days', 
                     iterations = n.iter, 
                     burnin = n.burn, 
                     thin = n.thin)


if(data.year == '2016'){
  model.site <- 'SN east side cells'
}else if(data.year == '2017'){
  model.site <- 'Humphreys Basin'
}else if(data.year == '2018'){
   model.site <- 'Mono creek'
}else if(data.year == '2019'){
  model.site <- 'Ritter Range'
}else{
  model.site <- '*****'
}

```
<br/>


<h4>Year: &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; `r data.year`</h4>
<h4>Species:  &nbsp;&nbsp;&nbsp;&nbsp;  `r sp`</h4>
<h4>Study Site:  &nbsp;&nbsp;  `r model.site`</h4>



<br><br/>

<h4>Metadata Summary:</h4>
```{r, echo = F}
## look at the metadata
kable(meta.summary,align = 'c') %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")



```

<br><br/>

<h4>WAIC</h4>
Models by WAIC:
```{r, echo = F}
### first look at the models by waic:

models.waic<-c(unlist(lapply(model.results, function(x) x$WAIC)))
waic.table<-tibble(model = models, description = descriptions, WAIC = models.waic) %>% 
  filter(!grepl('reverse', description)) %>% 
  arrange(WAIC)

kable(waic.table) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```

<br><br/>

<h4>Reversible Jump MCMC:</h4>
```{r, echo = F, results='asis'}

# rev.models<-model.results[grepl('fm9', names(model.results)) | grepl('fm10', names(model.results))]
rev.model.names<-models[grepl('reversible', descriptions) ]
# rev.names<-names(rev.models)
rev.models<-model.results[names(model.results) %in% rev.model.names]


rev.ind.list<-lapply(rev.models, function(x) x$samples[,grepl('ind', colnames(x$samples))])
rev.ind.means<-lapply(rev.ind.list, function(x) apply(x,2,mean))

# tables<-as.list(rep(NA,3))
# for(i in 1: length(rev.ind.means)){
#   label<-names(rev.ind.means[i])
#   model<-descriptions[[label]]
#   sum.temp<-tibble(cov = names(rev.ind.means[[i]]), indicator_mean = round(rev.ind.means[[i]],5)) %>% 
#     arrange(-indicator_mean)
#   cat(label,'    model:',model,'\n')
#   temp.tab<-kable(sum.temp) %>%
#     kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
#   print(temp.tab)
# }
  i=1
 label<-names(rev.ind.means[i])
  model<-descriptions[[label]]
  sum.temp<-tibble(cov = names(rev.ind.means[[i]]), indicator_mean = round(rev.ind.means[[i]],5)) %>%
    left_join(cov.alpha, by = c('cov')) %>% 
    select(cov, covariate, indicator_mean) %>% 
    arrange(-indicator_mean)
  cat(label,'    model:',model,'\n')
  
  sum.temp %>% 
    mutate(covariate = cell_spec(covariate, color = ifelse(indicator_mean >= .2, 'red', 'gray' ))) %>% 
    kable(escape = F) %>%
    kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

  
```

<br><br/>
<br><br/>
<div>

<h3>Model summaries:</h3>

```{r, include = F}
#############################################################################################################################
## model sc.fm1
plot.model<-models[[1]]
plot.dat<-model.results[[plot.model]]$samples[,c('psi', 'p') ]
#colnames(plot.dat<-model.results[[plot.model]]$samples)
plot.mcmc<-as.mcmc(plot.dat)
plot.gg<-ggs(plot.mcmc)
model.names<-colnames(plot.dat)

```


<h3>`r plot.model` &nbsp;&nbsp; summary:</h3>
`r descriptions[plot.model]`


###  {.tabset}

#### summary table

```{r, child = './_child_bayesOut_sumTable_tabs.Rmd', as.is = T}
```

#### `r in.param<-model.names[[1]]; in.param`

```{r, child = './_child_baysPlots_tabs.Rmd', as.is = T}
```

#### `r in.param<-model.names[[2]]; in.param`

```{r, child = './_child_baysPlots_tabs.Rmd', as.is = T}
```

###



<br><br><br>


```{r, include = F}
#############################################################################################################################
## model sc.fm2
plot.model<-models[[2]]
plot.dat<-model.results[[plot.model]]$samples[,c('psi', 'alpha0', paste0('alpha[',c(1:8), ']')) ]
plot.mcmc<-as.mcmc(plot.dat)
plot.gg<-ggs(plot.mcmc)
temp.names<-tibble(mod.names = colnames(plot.dat)) %>% 
  left_join(cov.alpha, by = c('mod.names' = 'alpha')) %>% 
  mutate(covariate = ifelse(is.na(covariate), mod.names, covariate))
model.names<-colnames(plot.dat)
print.name<-c(temp.names$covariate)
```


<h3>`r plot.model` &nbsp;&nbsp; summary:</h3>
`r descriptions[plot.model]`

###  {.tabset}

#### summary table

```{r, child = './_child_bayesOut_sumTable_tabs.Rmd', as.is = T}
```

#### `r i <- 1 ; in.param<-model.names[[i]]; print.name[i]`

```{r, child = './_child_baysPlots_tabs.Rmd', as.is = T}
```

#### `r i <- 2 ; in.param<-model.names[[i]]; print.name[i]`

```{r, child = './_child_baysPlots_tabs.Rmd', as.is = T}
```

#### `r i <- 3 ; in.param<-model.names[[i]]; print.name[i]`

```{r, child = './_child_baysPlots_tabs.Rmd', as.is = T}
```

#### `r i <- 4 ; in.param<-model.names[[i]]; print.name[i]`

```{r, child = './_child_baysPlots_tabs.Rmd', as.is = T}
```

#### `r i <- 5 ; in.param<-model.names[[i]]; print.name[i]`

```{r, child = './_child_baysPlots_tabs.Rmd', as.is = T}
```

#### `r i <- 6 ; in.param<-model.names[[i]]; print.name[i]`

```{r, child = './_child_baysPlots_tabs.Rmd', as.is = T}
```

#### `r i <- 7 ; in.param<-model.names[[i]]; print.name[i]`

```{r, child = './_child_baysPlots_tabs.Rmd', as.is = T}
```

#### `r i <- 8 ; in.param<-model.names[[i]]; print.name[i]`

```{r, child = './_child_baysPlots_tabs.Rmd', as.is = T}
```

#### `r i <- 9 ; in.param<-model.names[[i]]; print.name[i]`

```{r, child = './_child_baysPlots_tabs.Rmd', as.is = T}
```

#### `r i <- 10 ; in.param<-model.names[[i]]; print.name[i]`

```{r, child = './_child_baysPlots_tabs.Rmd', as.is = T}
```

###



